\bf Range Analysis for the IonMonkey JavaScript engine

### 2012-05-01 project-writings/paper.tex
Talk about our algorithm more

Our algorithm for range analsis is based on the algorithm due to Gough. It
differs from the paper in a few ways to better fit the architecture of
IonMonkey. The paper suggests using a dominator tree order, but we found that
using reverse post-order was better for our purposes: reverse post-order
traversal is simpler to implement in IonMonkey, and in general definitions are
still visited before all their uses. There is no issue of correctness since we
iterate until no range information is changing..

@@

>>>>

Our algorithm for range analsis is based on the algorithm due to Gough. It
differs from the paper in a few ways to better fit the architecture of
IonMonkey. The paper suggests using a dominator tree order, but we found that
using reverse post-order was better for our purposes: reverse post-order
traversal is simpler to implement in IonMonkey, and in general definitions are
still visited before all their uses. There is no issue of correctness since we
iterate until no range information is changing.

@@

SSA form lets us use a ``sparse'' analysis in which we only recompute
information that changes. This furthermore means that the runtime of our
SSA-based algorithm is bounded by the number of loop backedges in the graph: in
a graph with no back edges, on the second iteration we will discover that no
range information has changed and terminate the pass.

This method for performing range propagation has the added benefit that at
every iteration of the algorithm, the range information is correct. Additional
iterations serve only to yield more information. This is beneficial to
IonMonkey since there are plans to implement a ``base-line'' compiler which
performs small, cheap optimizations such as pessimistic global value numbering,
which runs in a single pass. When code becomes hot, it can be recompiled with
more expensive optimziations enabled. We will be able to run range analysis for
a few iterations in the base-line compilation mode, and run to a fixed point
when performing more aggressive optimization.
